Example bulk RNA-seq analysis 1

### 2024-09-11 dataprep/bulkrna1.Rmd
adding thread control to data prep

suppressPackageStartupMessages({
  library("getDEE2")
  library("DESeq2")
  library("clusterProfiler")
  library("mitch")
  library("kableExtra")
  library("eulerr")
  library("biomaRt")
})

>>>>

suppressPackageStartupMessages({
  library("getDEE2")
  library("DESeq2")
  library("clusterProfiler")
  library("mitch")
  library("kableExtra")
  library("eulerr")
  library("biomaRt")
  library("RhpcBLASctl")
})

RhpcBLASctl::blas_set_num_threads(1)
